BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2017-03-29 Paper2/BOAST.tex
Answers point 3) of the review.

The optimization parameters selected are not the same for those architectures.
Indeed, the Intel CPU favors kernels that have the parameters,
\emph{x\_compo-nent\_number} = 16, \emph{vector\_length} = 8,
\emph{temporary\_size} = 2 and \emph{synthesize\_loads} = false. Once again
\emph{vector\_recompute} does not apply. \emph{y\_component\_number} varies
from 4 to 2 when image size increase, thus decreasing task granularity as the
global work size increase. This result is unexpected and understanding why this
happen could be interesting. The NVIDIA GPU favors processing square tiles:
\emph{x\_component\_number} = 4, \emph{y\_component\_number} = 4,
\emph{vector\_length} = 4, \emph{temporary\_size} = 2 and
\emph{synthesize\_loads} = false. Once more, \emph{vector\_recompute} has no
meaning.

>>>>

The optimization parameters selected are not the same for those architectures.
Indeed, the Intel CPU favors kernels that have the parameters,
\emph{x\_compo-nent\_number} = 16, \emph{vector\_length} = 8,
\emph{temporary\_size} = 2 and \emph{synthesize\_loads} = false. Once again
\emph{vector\_recompute} does not apply. \emph{y\_component\_number} varies
from 4 to 2 when image size increase, thus decreasing task granularity as the
global work size increase. This result is interesting because its unexpected
nature strongly backs the use of autotuning. The NVIDIA GPU favors processing
square tiles: \emph{x\_component\_number} = 4, \emph{y\_component\_number} = 4,
\emph{vector\_length} = 4, \emph{temporary\_size} = 2 and
\emph{synthesize\_loads} = false. Once more, \emph{vector\_recompute} has no
meaning.
